\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts
\usepackage[]{fontawesome}
\setitemize[1]{itemsep=0pt,partopsep=0pt,parsep=\parskip,topsep=0pt}
\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Xunzhi Wen}

\basicInfo{
  \email{wenxunzhi7@gmail.com} \textperiodcentered\ 
  \phone{(+86) 17305527206}
  }

\section{Education}
\datedsubsection{\textbf{Xi'an Jiaotong University (XJTU)} \texorpdfstring{\quad}   GGPA:3.72/4.0}{Xi'an, China}
\textit{Bachelor of Science} in Information and Computing Sciences (ICS) \hfill Aug. 2019 -- Present 
\\Relevant Courses: Machine Learning (96), Abstract Algebra (93), Object-Oriented and Data Analysis（C\#）(93), Functions of real variable (92), Mathematical Statistics (90), Numerical Analysis (88)\\
\textbf{Honors and Awards}
\begin{itemize}
  \item \datedline{\textit{\nth{1} Prize}, TengFei Cup Innovation and Entrepreneurship Competition (56/572) }{2021}
  \item \datedline{\textit{Hounorable Mention}, Mathematical Contest In Modeling (30\%)}{2021, 2022}
  \item \datedline{\textit{\nth{3} Prize}, School Scholarship (10/37)}{2020, 2021}
  \item \datedline{\textit{Outstanding Volunteer}, Model United Nations Conference of China (10/150)}{2019}
\end{itemize}




\section{Research Experience}
\datedsubsection{\textbf{Expectation-induced modulation of metastable 
activity}}{Xi'an, China}
\role{R.A.}{Supervisor: \textit{Prof. Zigang Huang, School of Life Science and Technology}\hfill Jun. 2021 -- Present}
\begin{itemize}
  \item Applied the mean field theory to describe the global state, potential state and related parameters of network behavior when the model runs with input
  \item Defined a series of model evaluation indexes such as sequence entropy and decision sensitivity
  \item Tested the model with different stimuli and deciphered the graphs of state 
  \item Rated as a provincial project, winning Second Prize (5/40)
\end{itemize}
\datedsubsection{\textbf{Field research based policy analysis of rural agricultural cooperatives}}{Xi'an, China}
\role{R.A.}{Supervisor: \textit{Prof. Cong Li, School of Economics and Finance} \hfill Jun. 2020 -- Apr. 2021}
\begin{itemize}
  \item Conducted thorough background investigation over the topic
  \item Organized and implemented field research in different provinces
  \item Drafted data analysis and policy advice, wining First Prize (56 out of 572) 
\end{itemize}

\section{Work Experience}
\datedsubsection{\textbf{Lalamove Inc.}}{Shenzhen, China}
\role{Driver Management Intern}{Supervisor: \textit{Bingbing Yin, Vice-President}\hfill Aug. 2021 -- Sep. 2021} 
\begin{itemize}
  \item Assisted in designing driver's welfare and membership system
  \item Established reward and punishment system to normalize behaviours of drivers
  \item Designed credit score based driver welfare system 
  \item Participated in several interviews with drivers to collect opinions 
\end{itemize}
\section{Leadership Experience}

\datedsubsection{\textbf{Model United Nations Conference}}{Anhui, China}
\role{Dais Member}{Provicial Conference \hfill Apr. 2017 -- Aug. 2019}

\begin{itemize}
  \item Designed and drafted the background guide of conferences concerning global affairs
  \item Chaired the conference consisting of more than 50 delegates
  \item Checked and approved draft resolutions of delegates
\end{itemize}


\section{Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: C, Python, C\# ,MATLAB, \LaTeX, Microsoft Office
  \item Language: IELTS 8.0
  \item Interests: swimming, saxophone, badminton %最后不够再加上 
\end{itemize}

\end{document}
